Thermodynamic response functions in a cell fluid model

### 2024-09-11 paper_text.tex
adjusted figures according to ujp styleguide

Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\rho^*$ (see Fig.~\ref{fig1}a), and versus the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
\begin{figure}[h!]
	\centering 
	\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
	\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
	\vskip-3mm\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines. Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
	}\label{fig1}
\end{figure}

@@

\begin{figure}[htbp]
	%\centering 
	\includegraphics[width=0.5\textwidth]{f2a.pdf}
	%\includegraphics[width=\column]{f2a}
	%\vskip-3mm
	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
	}
	\label{fig2a}
\end{figure}

\begin{figure}[h!]
	\centering \includegraphics[width=0.45\textwidth]{f2b.pdf}
	\includegraphics[width=0.475\textwidth]{f2c.pdf}
	\vskip-3mm\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part~(a) covers a wider range of $M$. Part~(b) focuses on a range of $M$ around its critical value $0$.
	}\label{fig2b}
\end{figure}

@@

\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). The temperature dependence is weak, resulting in multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
	}\label{fig3a}
\end{figure}
\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}\label{fig3b}
\end{figure}
\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
	\vskip-3mm\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
	}\label{fig3c}
\end{figure}

@@

\begin{figure}[h!]
	\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}\label{fig4a}
\end{figure}

\begin{figure}[h!]
	\centering \includegraphics[width=0.45\textwidth]{f4b.pdf}
	\includegraphics[width=0.475\textwidth]{f4c.pdf}
	\vskip-3mm\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part (a) covers a wider range of $M$. Part (b) focuses on a range of $M$ around its critical value~$0$.
	}\label{fig4b}
\end{figure}

>>>>

Figure~\ref{fig1} shows the isotherms for the pressure $P^*$ versus density $\rho^*$ (see Fig.~\ref{fig1}a), and versus the effective chemical potential $M$ (see Fig.~\ref{fig1}b).
\begin{figure}[h!]
	%\includegraphics[width=0.446\textwidth]{f1a1.pdf} 
	%\includegraphics[width=0.45\textwidth]{f1b1.pdf} 
	\includegraphics[width=\column]{f1a1.pdf} 
	\includegraphics[width=\column]{f1b1.pdf}
	\vskip-3mm
	\caption{Isotherms of the reduced pressure $P^*$ as a function (a) of the density $\rho^*$, and (b) of the effective chemical potential $M$ at $T \geq T_c$ represented by black lines. Thick grey lines on both figures correspond to isotherms of pressure at $T < T_c$ based on the results taken from~\cite{KozlovskiiDobush2020}.
	}
	\label{fig1}
\end{figure}

@@

\begin{figure}[htbp]
	%\includegraphics[width=0.5\textwidth]{f2a.pdf}
	\includegraphics[width=\column]{f2a}
	\vskip-3mm
	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the density $\rho^*$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
	}
	\label{fig2a}
\end{figure}

\begin{figure}[h!] 
	%\includegraphics[width=0.45\textwidth]{f2b.pdf}
	%\includegraphics[width=0.475\textwidth]{f2c.pdf}
	\includegraphics[width=\column]{f2b.pdf}
	\includegraphics[width=\column]{f2c.pdf}
	\vskip-3mm
	\caption{The reduced isothermal compressibility $\kappa^*_T$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part~(a) covers a wider range of $M$. Part~(b) focuses on a range of $M$ around its critical value $0$.
	}
	\label{fig2b}
\end{figure}

@@

\begin{figure}[h!] 
	%\includegraphics[width=0.5\textwidth]{f3a.pdf}
	\includegraphics[width=\column]{f3a.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). The temperature dependence is weak, resulting in multiple isotherms collapsing onto the same line, making them indistinguishable at the scale of the figure.
	}
	\label{fig3a}
\end{figure}
\begin{figure}[h!]
	%\includegraphics[width=0.5\textwidth]{f3b.pdf}
	\includegraphics[width=\column]{f3b.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}
	\label{fig3b}
\end{figure}
\begin{figure}[h!]
	%\includegraphics[width=0.5\textwidth]{f3c.pdf}
	\includegraphics[width=\column]{f3c.pdf}
	\vskip-3mm
	\caption{The reduced thermal pressure coefficient $\beta^*_V$ as a function of the relative temperature $\tau$ at different values of the density $\rho^*$. 
	}
	\label{fig3c}
\end{figure}

@@

\begin{figure}[h!] 
	%\includegraphics[width=0.5\textwidth]{f4a.pdf}
	\includegraphics[width=\column]{f4a.pdf}
	\vskip-3mm
	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the density $\rho^*$ at different values of relative temperature $\tau > 0$~($T > T_c$). 
	}
	\label{fig4a}
\end{figure}

\begin{figure}[h!]
	%\includegraphics[width=0.45\textwidth]{f4b.pdf}
	%\includegraphics[width=0.475\textwidth]{f4c.pdf}
	\includegraphics[width=\column]{f4b.pdf}
	\includegraphics[width=\column]{f4c.pdf}
	\vskip-3mm
	\caption{The reduced thermal expansion coefficient $\alpha^*_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. Part (a) covers a wider range of $M$. Part (b) focuses on a range of $M$ around its critical value~$0$.
	}
	\label{fig4b}
\end{figure}
